\textls[-0]{\thetitle}

### 2023-03-15 metatheory-condensed.tex
More comments from Zhixuan

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families; they are like tuples composed of fields,
with field names represented by variable bindings.
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---the components preceding it.

>>>>

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families; they are like tuples composed of fields,
with field names represented by variable bindings.
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---the components preceding it.\Zhixuan{explain the intuition behind the (typing rule of) linkages, and try to connect it to the ``family'' in the earlier section/surface syntax}\EDJreply{I am not sure if more is needed because the section ``Family polymorphism via linkages'' is trying to do this. Maybe I should estabilish connection between Rule l/add with the compilation process of fam poly?}
